%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Ricardo}{Barrué}
\position{PhD researcher at \href{https://www.lip.pt/}{Laboratório de Instrumentação e Física Experimental de Partículas (LIP)} and \href{https://tecnico.ulisboa.pt/en/}{Instituto Superior Técnico (IST)}}
\address{LIP: Av. Prof. Gama Pinto, n.2, 1649-003 Lisboa, Portugal; IST: Av. Rovisco Pais, 1, 1049-001 Lisboa, Portugal}

\email{ricardo.barrue@cern.ch}
%\dateofbirth{January 1st, 1970}
% \homepage{www.posquit0.com}
\github{rbarrue}
\linkedin{ricardo-barrue}
\gitlab{rcoelhob}
\orcid{0000-0001-8985-5379}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Judith Katzy}
  {Deutsches Elektronen-Synchrotron DESY \\ Notkestraße 85 \\ 22607 Hamburg}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Postdoctoral Researcher}
% How the letter is opened
\letteropening{Dear Dr. Katzy,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Ricardo Barrué ~~~·~~~ Motivation Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my strong interest in the postdoctoral researcher position related to the NEEDLE project. This interdisciplinary project at the intersection of statistical inference, machine learning, software development and High-Energy Physics (HEP), aligns perfectly with my research and career goals.

There are deep questions for which the Standard Model (SM) does not provide an answer, such as the observed value of the baryonic asymmetric of the Universe or the origin of electroweak symmetry breaking. One of the most effective ways to answer such questions is via extremely precise measurements of SM processes, where effects from new physics may lead to tiny deviations, which is what I want to focus on. Furthermore, processes with large cross-sections and available datasets are excellent "playgrounds" to explore machine-learning-based techniques such as multi-dimensional unfolding or simulation-based inference (SBI), both of which I am very keen to explore.

I am eager to contribute to developing new statistical methods and software tools based on good programming practices. The challenge of designing such tools to exploit distributed computing systems, reducing time to insight, is also very appealing to me.

My background has prepared me well for such research. I am currently leading the first ATLAS search for CP-violating BSM components in the HWW vertex in $W(\to \ell \nu)H(\to b\bar{b})$ production, building on my contribution to the latest ATLAS VH production measurement (\href{https://arxiv.org/abs/2410.19611}{arXiv:2410.19611}). I have hands-on experience with the application of SBI methods, as the main author of a paper applying them to probe the interaction between the W and Higgs bosons, published in \href{http://dx.doi.org/10.1007/JHEP04(2024)014}{JHEP04(2024)014}. I also have substantial experience with trigger systems, as I contributed to the upgrade of the ATLAS Run 3 jet-based software trigger and served as trigger online expert on-call. During my research, I also developed experience in collaborative work, research strategy definition, supervision of students and science communication.

I have experience with the C++ and Python programming languages and collaborative software development tools such as Git/GitLab, commonly used in different steps of ATLAS analyses. I also have experience with SLURM-based distributed computing systems, which I used extensively for the development of the work in \href{http://dx.doi.org/10.1007/JHEP04(2024)014}{JHEP04(2024)014}. During my research, I also developed experience in collaborative work, research strategy definition, and technical supervision of students.

My skills and experience, combined with my enthusiasm and desire to learn, make me a strong candidate for this position. Thank you for your consideration, I look forward to discussing how I can contribute to your team and this innovative project.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
