\begin{cventries}

    \cventry
    {LIP}
    {Student Researcher (masters) - ATLAS group}
    {}
    {Sep. 2017 - Apr. 2020}
    {
        \textbf{Search for BSM CP-violating components in HWW interaction in WH production}\vspace{12pt}
        \begin{cvitems}      
            \item {showed that a measurement of WH production cross-section at very high transverse momenta (based on the ATLAS analysis of the same process) is not sensitive to CP-violating components.}
        \end{cvitems}
    }

    \cventry{LIP}
    {Research Internship - ATLAS group}
    {}
    {Sep. 2016 - Nov. 2016}
    {   
        \textbf{Calorimeter cluster reconstruction with GPU algorithms at the High-Level Trigger}\vspace{14pt}
        \begin{cvitems}
            \item {developed Python and Bash scripts to benchmark CPU/GPU algorithms, determining the most performant algorithm (GPU) and the most cost-effective combination of hardware resources.}
        \end{cvitems}
    }

    \cventry{LIP}
    {Research Internship - CMS group}
    {}
    {Jul. 2016}
    {
        \textbf{Searches of Higgs boson pair production with Boosted Decision Trees}\vspace{14pt}
        \begin{cvitems}
            \item {explored Principal Component Analysis and Gaussian standardization for input variables, leading to a large improvement in performance after retraining (AUROC $97.7\% \to 99.9\%$).}
        \end{cvitems}
    }

    \cventry{Institute for Plasmas and Nuclear Fusion (IST)}
    {Research Internship - Control Systems Engineering}
    {}
    {Jul. 2015}
    {Implemented the control system for a remote-controlled radiation physics experiment using DSPIC microcontrollers.}

\end{cventries}