\begin{cventries}
    
    \cventry{CERN International Masterclasses - Hands-on particle physics}{}
    {}{Mar. 2024}
    {Assistant on activity introducing experimental particle physics and CERN to high-school students.}

    \cventry{European Researcher's Night}{}
    {}{Sep. 2023}
    {Part of the LIP team, I used an Augmented Reality animation of collisions inside ATLAS to talk about ATLAS and the Standard Model to the general public (from 8 to 80+ years old!).} 

    \cventry{CERN International Masterclasses - Hands-on particle therapy}{}
    {}{Jun. 2021}
    {Assistant on activity to give high-school students a hands-on experience planning cancer treatments using photons, protons, or carbon ions.}

    \cventry{European Researcher's Night}{}
    {}{Nov. 2020}
    {Debate with LIP colleagues about technological applications and the future of particle physics.} 

    \cventry{MEFT Student Seminars}{}
    {}{May. 2020}
    {\href{https://www.youtube.com/watch?v=LSVwibOst74}{Seminar} (in Portuguese) to an audience of undergraduate physics students on the motivation and work done in my master thesis.}

    \cventry{40th PubHD Lisbon: The Infinitely Small}{}
    {}{Dec. 2019}
    {Short presentation of my master thesis work to a non-expert audience (in a pub).}

    \cventry{Study of anomalous Spin/CP components on the Higgs coupling to W pairs with the ATLAS detector}{}
    {}{Jul. 2018}
    {\href{https://youtu.be/gYDkRYdr_D4}{YouTube video} introducing my master thesis work.}

    \cventry{Physics on Wheels}{}
    {}{Jul. 2016}
    {Travelling physics exhibition, stopping at different places throughout Portugal to demonstrate simple physics experiments to both children and elders.}

\end{cventries}