\cvsubsection{Conferences}

\begin{cventries}

\cventry{Simulation-based inference in the search for CP violation in leptonic WH production}
{}
{}
{}
{
    \begin{cvitems}
    \item Talk at \href{https://indico.cern.ch/event/1230456/\#5-simulation-based-inference-i}{LHC Higgs Working Group WG2 and WG3 Extended Higgs Sector joint meeting on CPV in Higgs sector}
    \end{cvitems}
}

\end{cventries}

\cvsubsection{ATLAS internal workshops}

\begin{cventries}

\cventry{CP violation in WWH interactions with angular observables using the W(lv)H(bb) process}
{}
{Oct. 2023}
{\href{https://indico.cern.ch/event/1280531/contributions/5559532/}{ATLAS Higgs group Workshop}}{}

\cventry{The ATLAS jet trigger in Run 3}
{Poster presentation}
{Oct. 2022}
{\href{https://indico.cern.ch/event/1187086/\#37-the-atlas-jet-trigger-in-ru}{ATLAS Collaboration Week}}
{}

\end{cventries}

\cvsubsection{Other}

\begin{cventries}

\cventry{Precision measurements in pp and heavy ion collisions}{}{}
{\href{https://indico.lip.pt/event/1744/}{Jornadas Científicas do LIP, Oct. 2024}}{}

\cventry{CP violation in the HWW interaction in WH production}{}{}
{\href{https://indico.lip.pt/event/1745/}{8th IDPASC/LIP student workshop, Oct. 2024}}{}

\cventry{Optimisation of search of CP violation in HWW interaction via WH production}{}{}
{\href{https://indico.lip.pt/event/1183/}{Jornadas Científicas do LIP, Jul. 2022}}{Poster presentation}

\cventry{The ATLAS jet trigger and the search for CP violation in WH production}{}{}
{\href{https://indico.lip.pt/event/1245/}{7th IDPASC/LIP student workshop, Jun. 2022}}{}

\cventry{Optimization of the search for CP violation in the Higgs-WW interaction}{}
{}{\href{https://indico.lip.pt/event/643}{10th IDPASC School, Sep. 2021}}{}

\cventry{Study of the Spin/CP properties of the Higgs coupling to W bosons with ATLAS at the LHC}{}
{}{\href{https://indico.lip.pt/event/699/}{6th IDPASC/LIP PhD Students Workshop, Jun. 2020}}
{}

\cventry{Sensitivity to HWW anomalous couplings at ATLAS}{}
{}{\href{https://indico.lip.pt/event/650/}{Jornadas Científicas do LIP, Feb. 2020}}
{Poster presentation}

\cventry{Study of the Lorentz structure of the hWW vertex with the ATLAS experiment}{}
{}{\href{https://indico.lip.pt/event/359/}{Jornadas Científicas do LIP, Feb. 2018}}
{Poster presentation} 

\end{cventries}