\cvsection{Trainings/schools}

\begin{cventries}
    \cventry{\href{https://indico.cern.ch/event/1234112/}{2023 CERN-Fermilab Hadron Collider Physics Summer School}}{}
    {}{CERN, Aug. 2023}
    {10-day school targeted at young postdocs and senior PhD students with lectures on all aspects of theoretical and experimental hadron collider physics and statistical methods for data analysis. Includes lectures as well as Q\&A and discussion sessions in small groups, guided by more senior physicists.}\vspace*{2mm}

    \cventry{\href{https://indico.lip.pt/event/643}{10th IDPASC School}}{}{}{Online, Sep. 2021}
    {School of the International Doctorate Network in Particle Physics, Astrophysics and Cosmology (IDPASC), with lectures and exercise sessions on all of the network's physics topics, data acquisition for collider experiments, and machine learning.}
    
    \cventry
    {\href{https://agenda.irmp.ucl.ac.be/event/4097/}{UCLouvain Intensive Course on Statistics for HEP}}{}
    {}{Online, Dec. 2020}
    {Week-long course introducing the most commonly used statistical methods for high energy physics, with theoretical lectures and exercise sessions.}\vspace*{2mm}
    
    \cventry{\href{https://indico.cern.ch/event/946584}{1st HEP C++ Course and Hands-on Training (SIDIS + HSF)}}{}
    {}{Online, Oct. 2020}
    {Week-long course introducing the C++ language, from basic to advanced topics, with theoretical lectures and exercise sessions.}\vspace*{2mm}
        
    \cventry{\href{https://indico.cern.ch/event/997566/}{Course on Physics at the LHC}}{}{}{Online, Mar. - Jul. 2019}
    {School organized by LIP and IST, targetting graduate-level students, with lectures covering all aspects of LHC physics and additional lectures on statistics.}

    \cventry{\href{https://indico.lip.pt/event/206/}{First Lisbon mini-school on Particle and Astroparticle Physics}}{}
    {}{Lisbon, Feb. 2016}
    {Provides undergraduate students a comprehensive introduction to the field, covering theoretical and experimental aspects.}\vspace*{2mm}

    \cventry{\href{http://plasmasurf.tecnico.ulisboa.pt/index.html}{PlasmaSurf}}{}
    {}{Oeiras, Jul. 2015}
    {Summer school on plasma physics, intense lasers and nuclear fusion, tailored for BSc/MSc engineering and physics students}

    \cventry{\href{https://quark.fis.uc.pt}{Projeto Quark}}{}
    {}{Coimbra, Jan. - Jun. 2013}
    {Excelence school of physics for high-school students, with a limited number of participants.}

\end{cventries}

